Fourmile

### 2022-09-13 fourmile_dataprocess.Rmd
not sure what I updated

rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
summary(niwot_compare$diff_mm)

#filter to look at sept - june
# niwot_winter_comp <- niwot_compare %>%
#   mutate(month = month(date)) %>%
#   filter(!month %in% c(6:8))
# 
# summary(niwot_winter_comp)
```

@@

rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
summary(niwot_prismshift$diff_mm)
```

@@

rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
summary(niwot_prismfrac$diff_prismfrac)
#NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
#pbias(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)

@@

rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
summary(srad_compare$diff)
```

@@

rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
summary(srad_shift1day$diff)
#pbias(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
```

@@

rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
summary(srad_fracshift$diff_prismfrac)
#pbias(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
```

@@

#summary(srad_fracshift)
rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
summary(niwot_daymet_comp$diff)
```

>>>>

rmse(niwot_compare$prism_mm, niwot_compare$snotel_mm)
bias(niwot_compare$snotel_mm, niwot_compare$prism_mm)
summary(niwot_compare$diff_mm)
#filter to look at sept - june
# niwot_winter_comp <- niwot_compare %>%
#   mutate(month = month(date)) %>%
#   filter(!month %in% c(6:8))
# 
# summary(niwot_winter_comp)
```

@@

rmse(niwot_prismshift$prism_mm, niwot_prismshift$snotel_mm)
bias(niwot_prismshift$snotel_mm, niwot_prismshift$prism_mm)
summary(niwot_prismshift$diff_mm)
```

@@

rmse(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
bias(niwot_prismfrac$snotel_mm, niwot_prismfrac$prism_new_mm)
summary(niwot_prismfrac$diff_prismfrac)
#NSE(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)
#pbias(niwot_prismfrac$prism_new_mm, niwot_prismfrac$snotel_mm)

@@

rmse(srad_compare$prism_w, srad_compare$niwot_flux_mjm2)
bias(srad_compare$niwot_flux_mjm2, srad_compare$prism_w)
summary(srad_compare$diff)
```

@@

rmse(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
bias(srad_shift1day$niwot_flux_mjm2, srad_shift1day$prism_w)
summary(srad_shift1day$diff)
#pbias(srad_shift1day$prism_w, srad_shift1day$niwot_flux_mjm2)
```

@@

rmse(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
bias(srad_fracshift$niwot_flux_mjm2, srad_fracshift$prism_new)
summary(srad_fracshift$diff_prismfrac)
#pbias(srad_fracshift$prism_new, srad_fracshift$niwot_flux_mjm2)
```

@@

#summary(srad_fracshift)
rmse(niwot_daymet_comp$daymet_mjm2, niwot_daymet_comp$niwot_flux_mjm2)
bias(niwot_daymet_comp$niwot_flux_mjm2, niwot_daymet_comp$daymet_mjm2)
summary(niwot_daymet_comp$diff)
